\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-30 tex/paper.tex
small things

We begin with a family of data generation processes $p(X,Y,Z)$, where $X$ are the data, $Y$ are the target labels, and $Z$ are the nuisance parameters that can be continuous or categorical. We can use this model to generate training data for $X$ conditional on both $Y$ and $Z$. Our goal is to learn a predictive model $f(\cdot;\theta_f) : \mathbb{R}^p \mapsto {\cal S}$ of
parameters $\theta_f$ (e.g., a neural network-based probabilistic classifier) and minimizing  a loss ${\cal L}_f(\theta_f)$ (e.g.,
the cross-entropy).

In addition, we would like that inference based on $f(X ; \theta_f)$ should be
robust to the value $z$ of the nuisance parameter  -- which remains unknown at
test time. A formal way of enforcing robustness is to require that the distribution of 
$f(X ; \theta_f)$ conditional on $Z$ (and possibly $Y$) be invariant to the value $Z$
 of the nuisance parameter. Thus, we wish find a predictive function $f$ such that
\begin{equation}\label{eqn:criterion}
    p(f(X ; \theta_f) = s | z ) = p(f(X ; \theta_f) = s | z^\prime )
\end{equation}
for all $z,z^\prime \in  {\cal Z}$ and all values $s \in {\cal S}$ of $f(X ; \theta_f)$.
In words, we are looking for a predictive function $f$
which is a pivotal quantity \citep{degroot1986probability} with respect to the
nuisance parameter. That is, such that  the distribution of $f(X_z; \theta_f)$
is invariant with respect to the value $z$ of the nuisance.

>>>>

We begin with a family of data generation processes $p(X,Y,Z)$, where $X$ are
the data, $Y$ are the target labels, and $Z$ are the nuisance parameters that
can be continuous or categorical. We can use this model to generate training
data $\{x_i, y_i, z_i\}_{i=1}^N$ for $X$ conditional on both $Y$ and $Z$. Our goal is to learn a predictive
score function $f(\cdot;\theta_f) : \mathbb{R}^p \mapsto {\cal S}$ of parameters
$\theta_f$ (e.g., a neural network-based probabilistic classifier) and
minimizing  a loss ${\cal L}_f(\theta_f)$ (e.g., the cross-entropy).

In addition, we would like that inference based on $f(X ; \theta_f)$ should be
robust to the value $z \in {\cal Z}$ of the nuisance parameter $Z$  -- which remains unknown at
test time. A formal way of enforcing robustness is to require that the distribution of
$f(X ; \theta_f)$ conditional on $Z$ (and possibly $Y$) be invariant to the value
 of the nuisance parameter $Z$. Thus, we wish find a predictive function $f$ such that
\begin{equation}\label{eqn:criterion}
    p(f(X ; \theta_f) = s | z ) = p(f(X ; \theta_f) = s | z^\prime )
\end{equation}
for all $z,z^\prime \in  {\cal Z}$ and all values $s \in {\cal S}$ of $f(X ; \theta_f)$.
In words, we are looking for a predictive function $f$
which is a pivotal quantity \citep{degroot1986probability} with respect to the
nuisance parameter. That is, such that  the distribution of $f(X_z; \theta_f)$
is invariant with respect to the value $z$ of the nuisance.
